Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1031

We want to prove the following Lemma
\begin{lem}\label{lemma2_13}
Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function such that $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$ Then for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exist $C_4>0$ such that there is
\begin{align}
    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_4 \exp(\beta(\ln f(t)-\alpha t)), \quad t\geq 0.
\end{align}
\end{lem}
\begin{proof}
 Without loss of generality, we assume that $\|\mu\|=1$, By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|)}]\\
    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
\end{align*}
Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t},~ t\geq 0,\lambda\geq0$, $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
\begin{align*}
    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\cdot\left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right|\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t}\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}
\end{align*}
Therefore,
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}\cdot \frac{1}{1-e^{-\alpha^*}} e^{\lambda f(t)}.
\end{align*}
Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\cdot\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}\exp(\beta(\ln f(t)-\alpha t))
\end{align*}
Notice that
\begin{align*}
    w_t(s)^{-1/\beta-1}&\leq \frac{1}{(\alpha s^{-\beta}e^{-\alpha \beta t})^{1/
    \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.
\end{align*}
This is to say
\begin{align*}
    \sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}&\leq\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}
\end{align*}
We conclude the lemma by taking $C_4= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
\end{proof}
\begin{lem}\label{lemma28}
  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C_5>0$ and $\delta_1>0$ such that
  $$\mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq C_5 e^{-\delta_1 t},\quad t\geq 0.$$
\end{lem}

\begin{proof}
    First, for any $\epsilon>0$, using Markov inequality, we get
    $$\mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)\leq e^{-\epsilon t}.$$
    For another side, using Lemma \ref{lemma2_13}, we have
    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq C_4 e^{-\beta\epsilon t}, $$
Therefore,
\begin{align*}
    \mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq \mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq(C_4+1)e^{-\beta \epsilon t }
\end{align*}
\end{proof}

@@

\begin{proof}
    We want to show the gap between $m_k[f]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$,
    $$|m_k[f]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}\left|(-i T^{\alpha}_s f)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
    As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(f)bt}$,  $\kappa(f)=\kappa(\phi)$ and $\kappa(f-\phi)\geq \kappa(f)+1$. The inequality \eqref{eq:semigroupineq} yields that for some $R_5\in\mathcal{P}$ we have
    \begin{align*}
        &|T_s^{\alpha}f|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \\
        &|T_s^{\alpha}(f-\phi)|\leq e^{(\alpha-(\kappa(f)+1)b)s}R_5(x), \quad s\geq0.
    \end{align*}
  Using Lemma \ref{lem: Lip of power function} and the condition $\alpha\beta=\kappa(f)b(1+\beta)$, we get
    $$|m_k[f]-m_k[\phi]|\leq2C_0\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R_5^{1+\beta}(x)~ds~\varphi(x)~dx\leq \frac{2C_0}{b}\langle R_5^{1+\beta},\varphi\rangle e^{-bk},$$

@@

In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.
 \begin{lem}\label{lemma31}
 Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(R^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
 \begin{align}
      \frac{M_k^t[f]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{align}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[f]\right].$$
 \end{lem}
\begin{proof}
Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and Let $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$, by Lemma \ref{lemma28}, there exists $\delta_1>0$ and $C_5>0$ such that 
    \begin{align}
    \label{eq:31step0}
        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right|
        \\ &\leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{A}^c_{t-k-1}(\epsilon_0))
        \leq 2C_5e^{-\delta_1(t-k-1)},\quad k\in \mathbb{N}, t>k.\label{lemma33q}
    \end{align}

    Let $v_{f_k}(x,\theta)=v_{f_k}(1,x,\theta),\tilde{v}_{f_k}(x,\theta)=\tilde{v}_{f_k}(1,x,\theta)$ for short. For any $k\in\mathbb{N}$ and $t>k$, we have
    \begin{align*}
        &\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})]\\
        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
        &=\mathbb{\tilde{P}}_{\mu}\left[\mathbb{\tilde{P}}_{\nu}\left[\exp\left(i\frac{\theta}{F_k(v)}(\langle T_k^{\alpha}f,X_1\rangle-\langle T_{k+1}^{\alpha}f,\nu\rangle)\right)\right]_{\nu=X_{t-k-1}}\right]\\
        &=\mathbb{\tilde{P}}_{\mu}\left[\exp\left(\langle v_{f_k}(\cdot,\frac{\theta}{F_k(X_{t-k-1})}),X_{t-k-1}\rangle-i\frac{\theta}{F_k(X_{t-k-1})}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\right)\right].
    \end{align*}

    Next, our aim now is showing that the on the event $\mathcal{A}_{t-k-1}(\epsilon_0)$, the characteristic functions of random variables on both sides in \eqref{limitdistribution1} are much the same. Let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. Then
    \begin{align*}
        &\left|\mathbb{\tilde{P}}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right|\\
        &=\bigg|\big(\mathbb{\tilde{P}}_{\mu}\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\\
        &-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}}(\epsilon_0)\bigg|\\
        &\leq \mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
        &+\mathbb{\tilde{P}}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right].
    \end{align*}
    The first equation holds because that $v_{f_k}-i\theta T_1^{\alpha}f_k=v_{f_k}-\tilde{v}_{f_k}+Z_{f_k}$. the inequality holds by triangular inequality.

Step 1.  We will show that for each $\mu \in\mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_6>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k$,
    \begin{align}
    \label{lemma31q}  
        \mathbb{\tilde{P}}_{\mu}\left[\left|\langle v_{g_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{g_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
    \end{align}
Combining with \eqref{eq:semigroupineq}, \eqref{eq:gcontrol1} and Lemma \ref{lemma2}, there exist $R_1^f,R_6>0$ such that
\begin{align}
    & |v_{f_k}(x,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(x,\tilde{\theta}_{t,k})|\leq |\tilde{\theta}_{t,k} e^{(\alpha-\kappa(f) b)k}|^{1+2\beta}R^f_1(x),\\
    & |T_t (R^f_1)(x)|\leq R_6(x), \quad x\in \mathbb{R}^d,t\geq 0, \theta \in \mathbb{R}.
\end{align}
%Let $R_1$ be the control function in Lemma \ref{lemma2}. According to \eqref{eq:semigroupineq}, there exists $R_6\in \mathcal{P}$, satisfying $|T_t %(R_1)(x)|\leq R_6(x)$, for each $t>0$ and $x\in \mathbb{R}^d$.

>>>>

We want to prove the following Lemma
\begin{lem}\label{lemma2_13}
Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function such that $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$ Then for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exist $C_4>0$ such that there is
\begin{align}
    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_4 \exp(\beta(\ln f(t)-\alpha t)), \quad t\geq 0.
\end{align}
\end{lem}
\begin{proof}
 Without loss of generality, we assume that $\|\mu\|=1$, By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|)}]\\
    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
\end{align*}
Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t},~ t\geq 0,\lambda\geq0$, $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
\begin{align*}
    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\cdot\left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right|\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t}\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}
\end{align*}
Therefore,
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}\cdot \frac{1}{1-e^{-\alpha^*}} e^{\lambda f(t)}.
\end{align*}
Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\cdot\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}\exp(\beta(\ln f(t)-\alpha t))
\end{align*}
Notice that
\begin{align*}
    w_t(s)^{-1/\beta-1}&\leq \frac{1}{(\alpha s^{-\beta}e^{-\alpha \beta t})^{1/
    \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.
\end{align*}
This is to say
\begin{align*}
    \sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}&\leq\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}
\end{align*}
We conclude the lemma by taking $C_4= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
\end{proof}
\begin{lem}\label{lemma28}
  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C_5>0$ and $\delta_1>0$ such that
  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_5 e^{-\delta_1 t},\quad t\geq 0.$$
\end{lem}

\begin{proof}
    First, for any $\epsilon>0$, using Markov inequality, we get
    $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq e^{-\epsilon t}.$$
    For another side, using Lemma \ref{lemma2_13}, we have
    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq C_4 e^{-\beta\epsilon t}, $$
Therefore,
\begin{align*}
    \mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq \mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq(C_4+1)e^{-\beta \epsilon t }
\end{align*}
\end{proof}

@@

\begin{proof}
    We want to show the gap between $m_k[f]$ and $m_k[\phi]$ is very small. By the definition of $m_k[g]$,
    $$|m_k[f]-m_k[\phi]|\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-\alpha s}\left|(-i T^{\alpha}_s f)^{1+\beta}-(-i T^{\alpha}_s \phi)^{1+\beta}\right|(x)~ds~\varphi(x)~ds.$$
    As $\phi$ is the eigenfunction of $T_t$ corresponding to the eigenvalue $e^{-\kappa(f)bt}$,  $\kappa(f)=\kappa(\phi)$ and $\kappa(f-\phi)\geq \kappa(f)+1$. The inequality \eqref{eq:semigroupineq} yields that for some $R_5\in\mathcal{P}$ we have
    \begin{align*}
        &|T_s^{\alpha}f|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \quad|T_s^{\alpha}\phi|\leq e^{(\alpha-\kappa(f)b)s}R_5(x), \\
        &|T_s^{\alpha}(f-\phi)|\leq e^{(\alpha-(\kappa(f)+1)b)s}R_5(x), \quad s\geq0.
    \end{align*}
  Using Lemma \ref{lem: Lip of power function} and the condition $\alpha\beta=\kappa(f)b(1+\beta)$, we get
    $$|m_k[f]-m_k[\phi]|\leq2C_0\int_{\mathbb{R}^d}\int_k^{k+1}e^{-bs}R_5^{1+\beta}(x)~ds~\varphi(x)~dx\leq \frac{2C_0}{b}\langle R_5^{1+\beta},\varphi\rangle e^{-bk},$$

@@

In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.

{\bf In Milos' paper, he says $e^{\theta^{1+\beta}e^{\alpha}m_k[f]}$ is a characteristic function, but no explanation.}
\begin{lem}
For any $x,y\in \mathbb{C}$, $|e^x-e^y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|$.
\begin{proof}
let $z=Re(y)+Im(x)$,
\begin{align}\label{estim}
    |e^x-e^y|\leq|e^x-e^z|+|e^z-e^y|\leq |e^{Re(x)}-e^{Re(y)}|+e^{Re(y)}|x-y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|.
\end{align}
\end{proof}
\end{lem}
\begin{lem}\label{lemma31}

 Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(R^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
 \begin{align}
      \frac{M_k^t[f]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{align}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[f]\right].$$
 \end{lem}
     Let $v_{f_k}(x,\theta)=v_{f_k}(1,x,\theta),\tilde{v}_{f_k}(x,\theta)=\tilde{v}_{f_k}(1,x,\theta)$ and $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any $k\in\mathbb{N}$ and $t>k$, we have
        &\mathbb{P}_{\mu}[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})]\\
        &=\mathbb{P}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
        &=\mathbb{P}_{\mu}\left[\exp\left(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\right)\right].\\
        \label{condition mean}
        &=\mathbb{P}_{\mu}\left[\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\right]\\
       To get the conclusion of Lemma \ref{lemma31}, it suffices to show that
           \mathbb{P}_{\mu}\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\right)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(\theta^{1+\beta}e^{\alpha}m_k[f]).
       Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and Let $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
        Recall that $\mathcal{A}_t(\epsilon_0)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\}$.
        &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c}\right]\right| \\
        &\leq\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\right|\\
        &+\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right|
         Let $c=|\theta^{1+\beta}e^{\alpha}m_k[f]|$. By lemma \ref{lemm28}, there exists $\delta_1>0$ and $C_5>0$ such that
            &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right| \\
            &\leq \mathbb{P}_{\mu}(D^c)\mathbb{\tilde{P}}_{\mu}(\mathcal{A}_{t-k-1})\leq (1+e^c)C_5\mathbb{P}_{\mu}(D^c)e^{-\delta_1(t-k-1)}.
       On the other hand, by formula \eqref{condition mean} and Lemma \ref{estim}
        &\left|\mathbb{P}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right|\\
        &\leq e^c\mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
        \label{ineqinlem31}
        &+e^c\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right].
Step 1.  We will show that for each $\mu \in\mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_6>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k$,
    \label{lemma31q}
        \mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
Combining with \eqref{eq:semigroupineq}, \eqref{eq:gcontrol1} and Lemma \ref{lemma2}, there exist $R_1^f,R_6>0$ such that
    & |v_{f_k}(x,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(x,\tilde{\theta}_{t,k})|\leq |\tilde{\theta}_{t,k} e^{(\alpha-\kappa(f) b)k}|^{1+2\beta}R^f_1(x),\\
    & |T_t (R^f_1)(x)|\leq R_6(x), \quad x\in \mathbb{R}^d,t\geq 0, \theta \in \mathbb{R}.
%Let $R_1$ be the control function in Lemma \ref{lemma2}. According to \eqref{eq:semigroupineq}, there exists $R_6\in \mathcal{P}$, satisfying $|T_t %(R_1)(x)|\leq R_6(x)$, for each $t>0$ and $x\in \mathbb{R}^d$.

For any $\theta\in \mathbb{R}$, $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}$, we have
        &\mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]
        \\ &\leq \left(\frac{|\theta|e^{(\alpha-\kappa(f)b)k}}{(e^{\alpha k}\|\mu\|e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\right)^{1+2\beta}\mathbb{\tilde{P}}_{\mu}\langle R^f_1,X_{t-k-1}\rangle\\
        &\leq\frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle R_6,\mu\rangle|\theta|^{1+2\beta}e^{\alpha(t-k-1)} e^{-\frac{\alpha(1+2\beta)(t-k-1)}{1+\beta}}e^{\frac{\epsilon_0(1+2\beta)(t-k-1)}{1+\beta}}\\
        &\leq \frac{1}{\|\mu\|^{(1+2\beta)/(1+\beta)}}\langle R_6,\mu\rangle|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
 Step 2. Let $h_k(x):=Z_{f_k}(x)-\langle Z_{f_k},\varphi\rangle,~x\in\mathbb{R}^d$.to prove inequality \eqref{ineqinlem31}, We will first show that there exists $R_7\in \mathcal{P}$ such that for any $k\in\mathbb{N}$, $x\in \mathbb{R}^d$ and $s\geq 0$,
 \label{eq:31step2}
     |T_s h_k(x)|\leq e^{-bs}e^{(\alpha-\kappa(f)b)(1+\beta)k}R_7(x).
